Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
pass over rw

Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}, e.g.,  on the minimization of failing tests through the identification of code components that do not contribute to the fault revelation. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and locate and contour faults of omission~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. 
%
% \subsection{SFL}
%
Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques. Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
fault localization technique used to rank faulty components ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. This technique uses tests coverage information to rank program's components. We suspect that several highly suspicious components—often involved in failing, but seldom in passing test runs—may be unrelated to the bug. Prior work has investigated the \ds{}-\sfl{} combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}. Overall,
these studies reported promissing results but based their conclusions on a very small group of faults and using different techniques. Although, \ds{} does not ensure the improvement of \sfl{} since it can remove faulty statements from the failing test, we believe it has a great potential to help reducing test cases and improve \sfl{} accuracy. In this study, a larger set of faults is evaluated and a more rigorous experimental methodology.

>>>>

Dynamic Slicing has found its main application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}, e.g.,  on the minimization of
failing tests through the identification of code components that do not
contribute to the fault revelation. Research in this area has mainly focused on
slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455} and
locate and contour faults of
omission~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}.

Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques. Spectrum-based fault
localization (\sfl{}) is amongst the most common statistical fault localization
technique used to rank faulty components
~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
This technique uses tests coverage information to rank program's components.
\Rui{this sentence does not belong to rw (We suspect...)-->} We
suspect that several highly suspicious components—often involved in failing, but
seldom in passing test runs—may be unrelated to the bug.

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
